### 2021-03-29 treatise-pdflatex/4_simulation.tex
Change dimension: context version

\Disp {
\Hat {\V {g}}
\leftarrow \Min {\V {g}' \in \mathbb {C} ^{N_H^2}}
\RB {\VNm {\V {g}'} _1 + \l \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty}
}

However, there is no simple way to determine the value of \m {\l} in advance.
We have tried basis pursuit denoising, with \m {\l = N_H^2 / \g_{\mathrm {DS}}} in the simulation.

@@

We use dimensionless noise level \m {\s} which takes value starting with \m {2^{-4}}, and being multiplied by powers of \m {2}, for \m {6} values.
We take \m {N_H} to be \m {6, 12, 18}, respectively.
For assorted plots, three series of plots are simulated.
The first series for \m {N_{H,t} = 2 N_B} and \m {N_{H,r} = 2 N_B}.
The second series for \m {N_{H,t} = 2 N_H} and \m {N_{H,r} = 3 N_H}.
The third series for \m {N_{H,t} = 3 N_H} and \m {N_{H,r} = 2 N_H}.
Unfortunately, this is very far from achieving the ideal values \eqref {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.

@@

For Lasso, \m {\g} (or \m {\l}) is also crucial to the performance, but cannot be obtained in advance.
Thus, for sake of comparison, we set the same threshold for Lasso and DS.
Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.

@@

We see that \m {\RB {\M {P} ^\dagger \V {z}} _{\SB {j}}} observes complex standard normal distribution.
If we agree that, for high probability,
%
\DispNum {O:j:sO:O1} {
\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}}}
= \s N_H^2 \mathcal {O} \RB {1} 
}
Then we simply have
%
\DispNum {C:S:ON:H6} {
C_{\mathrm {DS}}
=\mathcal {O} \SB {N_{H}^6} 
}

@@

Tropp and Gilbert \cite {TrG07a} discussed the complexity of OMP in the companion paper \cite {TrG07b}, giving
%
\DispNum {C:P:ON:NY} {
C_{\mathrm {OMP}}
=\mathcal {O} \SB {N_H^2 \log \RB {N_{B,r} N_{B,t}}}
}
%
Here \m {\log \RB {N_{B,r} N_{B,t}}} is small in our experiments, and if we dropped it, we may take
\DispNum {C:P:ON:H2} {
C_{\mathrm {OMP}}
=\mathcal {O} \SB {N_H^2}
}

@@

Lasso is equivalent to a quadratically constrained quadratic program, and there is not always a closed form for its complexity.
However, Lasso and DS are equivalent in certain conditions \cite {AsR10}, and we may suppose here they have the same complexity, \m {\mathcal {O} \SB {N_H^6}}.

@@

Therefore we take
\DispNum {C:o:ON:H6} {
C_{\mathrm {Lasso}}
=\mathcal {O} \SB {N_H^6}
}

@@

All plots included in this treatise, in total, took about one month to run.
Figures for \m {N_H = 18} each took about \m {3} days.
The computer has \m {32} GB RAM, and Intel Core i9 processor.
Simulation was run on Linux subsystem 2 of Windows 10.

Use \m {t_{\mathrm {OMP}} \SB {N_H}}, \m {t_{\mathrm {Lasso}} \SB {N_H}}, \m {t_{\mathrm {DS}} \SB {N_H}} to denote their respective time taken.
We here copy the arithmetic average (including different \m {\s}) of simulated values below, in seconds.
They are:
\m {t_{\mathrm {OMP}} \SB {12}  = 0.0119,}
\m {t_{\mathrm {OMP}} \SB {16} = 0.0297, }
\m {t_{\mathrm {OMP}} \SB {20}  = 0.0600,}
\m {t_{\mathrm {OMP}} \SB {24} = 0.155, }
%
\m { t_{\mathrm {Lasso}} \SB {12}  = 0.0436,}
\m { t_{\mathrm {Lasso}} \SB {16} = 0.176, }
\m { t_{\mathrm {Lasso}} \SB {20}  = 0.471,}
\m { t_{\mathrm {Lasso}} \SB {24} = 1.26, }
%
\m { t_{\mathrm {DS}} \SB {12}  = 0.357,}
\m { t_{\mathrm {DS}} \SB {16} = 2.07, }
\m { t_{\mathrm {DS}} \SB {20}  = 29.8,}
\m { t_{\mathrm {DS}} \SB {24} = 91.5}

Simulation illustrates that \m {t_{\mathrm {DS}}} grows tremendously with \m {N_H}, agreeing Friedlander and Saunders \cite {FrS07} who noted the high complexity of DS.
This is not surprising, since the inversion of \m {\M {P} \M {P} ^\Adj} is probably the bottleneck of complexity, which has dimension \m {\M {N}_H^2}.
By the way, different tolerance levels and maximal iteration numbers may result in vastly different computation time.

@@

\DispNum {t:P:NH:83} {
\tilde {t}_{\mathrm {OMP}} \eqsim &\mathcal {O} \SB {N_H^{3.6}} \\
\tilde {t}_{\mathrm {Lasso}} \eqsim &\mathcal {O} \SB {N_H^{4.8}} \\
\tilde {t}_{\mathrm {DS}} \eqsim &\mathcal {O} \SB {N_H^{8.3}} 
}

>>>>

\Disp {
\Hat {\V {g}}
\leftarrow \Min {\V {g}' \in \mathbb {C} ^{N_{H,t} N_{H,r}}}
\RB {\VNm {\V {g}'} _1 + \l \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty}
}

However, there is no simple way to determine the value of \m {\l} in advance.
We have tried basis pursuit denoising, with \m {\l = N_{H,t} N_{H,r} / \g_{\mathrm {DS}}} in the simulation.

@@

We use dimensionless noise level \m {\s} which takes value starting with \m {2^{-4}}, and being multiplied by powers of \m {2}, for \m {6} values.
We take \m {N_Y} to be \m {4, 6, 8}, respectively.
Three series of plots are simulated.
The first series for \m {N_{H,t} = 2 N_B} and \m {N_{H,r} = 2 N_B}.
The second series for \m {N_{H,t} = 2 N_B} and \m {N_{H,r} = 3 N_B}.
The third series for \m {N_{H,t} = 3 N_B} and \m {N_{H,r} = 2 N_B}.
Unfortunately, this is very far from achieving the ideal values \eqref {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.

@@

For Lasso, \m {\g _{\mathrm {Lasso}}} (or \m {\l _{\mathrm {Lasso}}}) is also crucial to the performance, but cannot be obtained in advance.
Thus, for sake of comparison, we set the same threshold for Lasso and DS.
Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.

@@

We see that \m {\RB {\M {P} ^\dagger \V {z}} _{\SB {j}}} observes complex standard normal distribution.
If we agree that, for high probability,
%
\DispNum {O:j:sO:O1} {
\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}}}
= \s N_{H,t} N_{H,r} \mathcal {O} \RB {1} 
}
Then we simply have
%
\DispNum {C:S:ON:H6} {
C_{\mathrm {DS}}
=\mathcal {O} \SB {N_{H,t} ^3 N_{H,r} ^3} 
}

@@

Tropp and Gilbert \cite {TrG07a} discussed the complexity of OMP in the companion paper \cite {TrG07b}, giving
%
\DispNum {C:P:ON:NY} {
C_{\mathrm {OMP}}
=\mathcal {O} \SB {N_{H,t} N_{H,r} \log N_B} 
}
%
Here \m {\log \RB {N_{B,r} N_{B,t}}} is small in our experiments, and if we dropped it, we may take
\DispNum {C:P:ON:H2} {
C_{\mathrm {OMP}}
=\mathcal {O} \SB {N_{H,t} N_{H,r}}
}

@@

Lasso is equivalent to a quadratically constrained quadratic program, and there is not always a closed form for its complexity.
However, Lasso and DS are equivalent in certain conditions \cite {AsR10}, and we may suppose here they have the same complexity, \m {\mathcal {O} \SB {N_{H,t} ^3 N_{H,r} ^3}}.

@@

Therefore we take
\DispNum {C:o:ON:H6} {
C_{\mathrm {Lasso}}
=\mathcal {O} \SB {N_{H,t} ^3 N_{H,r} ^3}
}

@@

All plots included in this treatise, in total, took about one month to run.
Figures for \m {N_{H,t}, N_{H,r} \geq 24} each took about \m {3} days.
The computer has \m {32} GB RAM, and Intel Core i9 processor.
Simulation was run on Linux subsystem 2 of Windows 10.

Abbreviate \m {N_h = N_{H,t} \D N_{H,r}} as in the last chapter.
Use \m {t_{\mathrm {OMP}} \SB {N_h}}, \m {t_{\mathrm {Lasso}} \SB {N_h}}, \m {t_{\mathrm {DS}} \SB {N_h}} to denote their respective time taken.
We here copy the arithmetic average (including different \m {\s}) of simulated values below, in seconds.
They are:
\m {t_{\mathrm {OMP}} \SB {12}  = 0.0119,}
\m {t_{\mathrm {OMP}} \SB {16} = 0.0297, }
\m {t_{\mathrm {OMP}} \SB {20}  = 0.0600,}
\m {t_{\mathrm {OMP}} \SB {24} = 0.155, }
%
\m { t_{\mathrm {Lasso}} \SB {12}  = 0.0436,}
\m { t_{\mathrm {Lasso}} \SB {16} = 0.176, }
\m { t_{\mathrm {Lasso}} \SB {20}  = 0.471,}
\m { t_{\mathrm {Lasso}} \SB {24} = 1.26, }
%
\m { t_{\mathrm {DS}} \SB {12}  = 0.357,}
\m { t_{\mathrm {DS}} \SB {16} = 2.07, }
\m { t_{\mathrm {DS}} \SB {20}  = 29.8,}
\m { t_{\mathrm {DS}} \SB {24} = 91.5}

Simulation illustrates that \m {t_{\mathrm {DS}}} grows tremendously with \m {N_h}, agreeing Friedlander and Saunders \cite {FrS07} who noted the high complexity of DS.
This is not surprising, since the inversion of \m {\M {P} \M {P} ^\Adj} is probably the bottleneck of complexity, which has dimension \m {\M {N}_H^2}.
By the way, different tolerance levels and maximal iteration numbers may result in vastly different computation time.

@@

\DispNum {t:P:NH:83} {
\tilde {t}_{\mathrm {OMP}} \eqsim &\mathcal {O} \SB {N_h^{3.6}} \\
\tilde {t}_{\mathrm {Lasso}} \eqsim &\mathcal {O} \SB {N_h^{4.8}} \\
\tilde {t}_{\mathrm {DS}} \eqsim &\mathcal {O} \SB {N_h^{8.3}} 
}

### 2021-03-29 treatise-pdflatex/foreword.tex
Change dimension: context version

I came across the field of compressive sensing in 2018, to begin with, when I was the TA of the course of Convex Optimization, and read about it again as an intern in MediaTek.
Prof.\ Su always had students find their own topic of interest, and I thank him for having encouraged me to continue writing what would become of this treatise, even if when I first told him of the proposal, it was hardly more than a stream of conciousness.
In addition to the stipend he kindly supplied, the warm faux-wood floor, comfortable sofas, and ergonomic chairs in the lab also helped.
For various reasons, I took very long time writing this treatise, and I thank the advisor for his tolerance on my procrastination, if that is not too late.

The present treatise is far from being remarkable, but I suppose the course of devising, clarifying, speculating, verifying, programming, debugging, googling, and polishing does teach some resilience to a weak mind.
The three and half years are punctuated by Bachi martial art practice session, teaching assistant's preparation and scoring, chess club meeting, MediaTek internship, and the two semester courses of Real Analysis and Advanced Statistical Inference, which are recollections I too hold dearly.

In addition, I thank Chu-Tong Liu, a fellow PhD student of Prof.\ Su's, who I have acquainted in the undergraduate freshman year, in that he gave me valuable suggestions when I was stuck, and was lenient when I did not, or even failed at all to, deliver a proper presentation.
I too cherish the decent meals, trips, and board games enjoyed together with fellow lab students, whose discussion, concern, joke, and sarcasm are particularly enlightening when one is undergoing a writer's block.

After all, I thank my parents, who in recent years was supportive of whatever goal I set up to do (or at least claimed to work on), if slightly too credulous in my ability.
It so was a tremendous luck that I did not have to mind financial matters in the master student years, which is something I ought to treasure.
I am happy to have kept a sense of curiosity for the intricate universe.

>>>>

I came across the field of compressive sensing in 2018, to begin with, when I was the TA of the course on convex optimization by Prof.\ Borching Su, and read about it again as an intern in MediaTek.
Prof.\ Hsuan-Jung Su always had students find their own topic of interest, and I thank him for having encouraged me to continue writing what would become of this treatise, even if when I first told him of the proposal, it was hardly more than a stream of consciousness.
In addition to the stipend he kindly supplied, the warm faux-wood floor, comfortable sofas, and ergonomic chairs in the lab are also impressive.
For various reasons, I took very long time writing this treatise, and I thank the advisor for his tolerance on my procrastination, if that is not too late.
And at my presentation, Prof.\ Borching Su and Prof.\ I-Hsiang Wang, the oral defense committee, gave a lot suggestions, which are equally indispensable.

The present treatise is far from being remarkable, but I suppose the course of devising, clarifying, speculating, verifying, programming, debugging, googling, and polishing does teach some resilience to a weak mind.
The three and half years are punctuated by Bachi martial art practice session, TA preparation and scoring, chess club meeting, MediaTek internship, and the two semester courses of Real Analysis and Advanced Statistical Inference, which are recollections I hold dearly.

In addition, I thank Chu-Tong Liu, a fellow PhD student, who I have acquainted in the undergraduate freshman year, in that he gave me valuable helps when I was stuck, and was lenient when I did not deliver a proper presentation.
I too cherish the decent meals, trips, and board games enjoyed together with lab students, whose discussion, concern, joke, and sarcasm are particularly enlightening when one is undergoing a writer's block.

After all, I thank my parents, who in recent years was supportive of whatever goal I set up to do (or at least claimed to work on), if slightly too credulous in my ability.
It so was a tremendous luck that I did not have to mind financial matters in the master student years.
Therefore, I am happy to have kept a sense of curiosity for the intricate universe.
